---
title: "Surrogacy and follow-up paper analyses Clarke"
author: "Mario Ouwens"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 4
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(survival)
library(flexsurv)
library(ggplot2)
library(doMC)
library(doRNG)
library("wCorr")

#for parallel programming
library(doMC)
library(doRNG)

registerDoMC(10)

n.cores <- 10
my.cluster <- parallel::makeCluster(
  n.cores, 
  type = "PSOCK"
  )
print(my.cluster)

#register it to be used by %dopar%
doParallel::registerDoParallel(cl = my.cluster)
foreach::getDoParRegistered()

#how many workers are available?
#foreach::getDoParWorkers()

```


#HbA1c

Data extracted from Clarke et al 2004
```{r HbA1c, include=FALSE}
Time	<- c(
0.167419937	,
0.397667099	,
0.627675601	,
0.77415313	,
0.962157486	,
1.213108396	,
2.885517817	,
1.902895243	,
2.383854656	,
3.303888665	,
3.617070151	,
4.076609836	,
4.452976537	,
5.05899375	,
5.601587088	,
6.039707045	,
6.394773348	,
6.74972032	,
7.104905953	,
7.501499083	,
7.897972882	,
8.294327352	,
8.691039811	,
8.941155412	,
9.316925464	,
9.734103012	,
9.963634194	,
10.27621903	,
10.5262153	,
10.73456542	,
10.9427962	,
11.1929118	,
11.48467356	,
11.67231992	,
11.85972763	,
11.96408168	)

Cum_death	 = c(
0.000569801	,
0.001139601	,
0.002849003	,
0.003418803	,
0.005698006	,
0.007407407	,
0.021652422	,
0.013675214	,
0.017094017	,
0.023931624	,
0.028490028	,
0.034188034	,
0.037037037	,
0.043304843	,
0.052421652	,
0.06039886	,
0.064957265	,
0.07008547	,
0.074074074	,
0.08034188	,
0.087179487	,
0.094586895	,
0.1002849	,
0.105982906	,
0.111680912	,
0.11965812	,
0.123646724	,
0.131054131	,
0.137321937	,
0.142450142	,
0.148148148	,
0.153846154	,
0.160683761	,
0.164672365	,
0.16980057	,
0.171509972	)

#check before ordering: 
#matcheck <- data.frame(matrix(nrow = length(Time), ncol = 2))
#matcheck[,1] <- Cum_death
#matcheck[,2] <- Time
#matcheck2 <- matcheck[order(matcheck[,1]),]
#table(matcheck2[,2] ==matcheck2[order(matcheck2[,2]),2])

#meaning Time and Cum_death can be ordened without generating wrong information

Time <- Time[order(Time)]
Cum_death <- Cum_death[order(Cum_death)]
```

Simplification death Time -> per 0.0001
```{r}
rm(Clarke)

Clarke <- data.frame(matrix(nrow = 10000, ncol = 2))
for(i in 1: 10000){

  #Computation rownumber for death percentage i/10000   
  start_d <- sum(Cum_death < i/10000)
  if (start_d>0){ 
  Clarke[i,1] <- i/10000
  #estimate of time point for death equal to i/10000
  Clarke[i,2] <- 
  (i/10000 - Cum_death[start_d])/(Cum_death[start_d+1]-Cum_death[start_d])*
  (Time[start_d+1]-Time[start_d])+
    Time[start_d]
  }
  if (start_d == 0){
  #for i/10000 smaller than first element in Cum_death
  Clarke[i,1] <- i/10000
  #time point for death i/10000
  Clarke[i,2] <- 
  (i/10000)/(Cum_death[1])*(Time[1])
  
  }
  
}


#To plot the end result.  
Clarke_plot <- Clarke
#from death to survival
Clarke_plot[,1] <- 1-Clarke_plot[,1]
names(Clarke_plot) <- c("Survival", "Time")

ggplot(data = Clarke_plot, mapping = aes(x = Time, y = Survival))+
  geom_point()+
  theme_bw() + 
  theme(panel.grid.minor = element_blank())

#saving figure
ggsave("plot_Clarke.jpeg")

#used when percentage sampled is above maximum percentage obtained from #Clarke. This would mean that the duration is longer than 11.96408. We only 
#evaluate for first 10 years

Clarke[,2]<-ifelse(is.na(Clarke[,2]), 1000, Clarke[,2])

#distance betwen two subsequent percentages
dist_Clarke <- Clarke[2,1] - Clarke[1,1]

#extra for time point 0 having 0 deaths 
Clarke <- rbind(c(0,0), Clarke)

#For computational simplicity
Clarke <- rbind(Clarke, c(1.1,1000))


```


#Basecase analyses 
```{r , include=FALSE}
set.seed(100)

#Rivera paper 
mean_HbA1c_effect <- -0.43
SD_HbA1c_effect <- 0.17
n_studies <- 19
#number per arm -> we assume equal studies in sample size
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000
#to have HR 0.8 as a mid point
beta <- 1.18

#dataset in which the results will be stored per duration
sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

a <- 
foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot")) %dorng% {
#empty matrix in which the iterations results will be stored
Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
#evaluation from 1 to 10 year

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)

for (duration in 1:10){
#empty dataset to store results in for the 10 durations
results <- data.frame(matrix(ncol = 3, nrow = 0))

#creating trials
for (trial in 1: n_studies){

#HbA1c effect from normal distribution
HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)

#Mapping from HbA1c to underlying ln HR 
ln_HR <- HbA1c_effect*beta
#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)

#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]

#From percentage to time:
#Row to be used for percentages
elt_Clarke1 <- trunc(pat1/dist_Clarke)+1

#linear interpolation to obtain time point
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> percentage under control can be computed given HR
#that control percentage can be searched for (minus for ln HR to get to control)
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
#element that pat2_1 is reached
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
#computation time by interpolation
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]

#if Time_pat < duration then death, otherwise censoring at duration
#here we cause thus that time points equal to 1000 are censored at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

Time_pat1 <- ifelse(Time_pat1 < duration, Time_pat1, duration)
Time_pat2 <- ifelse(Time_pat2 < duration, Time_pat2, duration)

data_Cox <- data.frame(time = c(Time_pat1, Time_pat2), 
                       cens = c(cens_pat1, cens_pat2), tx )  

#causing program to stop when something wrong is happening
if(min(data_Cox$time) < 0){
  print("time below 0")
    Problem
    return()
  
}

#Cox model
a <- coxph(Surv(data_Cox$time, 1-data_Cox$cens) ~ tx)

#storage of results
results <- rbind(results, c(HbA1c_effect, a$coefficients, a$var))

}


#Correlation. We use Pearson here as prediction is important. 
#weighted for 1/var
names(results) <- c("surrogate", "target", "target_var")

boot.func <- function(dat, indices) {
data1=dat[indices,]

res <- weightedCorr(
data1$surrogate,
data1$target,
method = "Pearson",
weights = 1/data1$target_var,
ML = FALSE,
fast = TRUE
)
}

res.boot <- boot(results, boot.func, R=1000)  

#Storing into overall-results for duration
Overall_results <- rbind(Overall_results, 
c(duration, median(res.boot$t), quantile(res.boot$t, 0.025),
  quantile(res.boot$t, 0.975)))
}

#Storing into data for the iterations
names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)

#returning duration, R, lower bound and upper bound
return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))

}

#a is created and is a list. 

R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  #2nd element is R, then every 4 times R is found back as list element in a
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
#aggregation over all iterations
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
#3rd element is R lower bound, then every 4 times R is found back as list element in a
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
#aggregation
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
#4th element is R upper bound, then every 4 times R is found back as list element in a
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
#aggregation over all iterations
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

write.csv(total_eval, "basecase1000.csv")

```


Plotting

```{r}

#Creating matrix in which results will be stored for plotting
total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

#R mean
total_eval2$Group[1:10]<- "R mean"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R_agg$x

#R lower bound
total_eval2$Group[11:20]<- "R LB"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R_LB_agg$x

#R upper bound
total_eval2$Group[21:30]<- "R UB"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- R_UB_agg$x

#plot
a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.43,0.73, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

#saving plot
ggsave("Basecase2.jpeg")

```

#Intermezzo Rivera analyses with only studies having more than 20 events
```{r , include=FALSE}
set.seed(100)

#Rivera paper 
mean_HbA1c_effect <- -0.43
SD_HbA1c_effect <- 0.17
n_studies <- 19
#number per arm -> we assume equal studies in sample size
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))

#to have HR 0.8 as a mid point
beta <- 1.18

#dataset in which the results will be stored per duration
sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

#creating results from the different iterations
a <- 
foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot")) %dorng% {
#empty matrix in which the iterations results will be stored
Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))


#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients

#evaluation from 1 to 10 year
for (duration in 1:10){

#empty dataset to store results in for the 10 durations
results <- data.frame(matrix(ncol = 3, nrow = 0))

#creating trials
#here we sample until we have the situation that we have the 19 studies
while (length(results[,1]) < n_studies){

#HbA1c effect from normal distribution
HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)

#Mapping from HbA1c to underlying ln HR 
ln_HR <- HbA1c_effect*beta

#creation of the survival percentages for the patients in the trial
pat1 <- runif(n_arm)
pat2 <- runif(n_arm)

#model to come from percentage to time:

#Control arm
elt_Clarke1 <- trunc(pat1/dist_Clarke)+1
#Interpolation
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> first % to control 
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
#interpolation
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]

#if Time_pat < duration then death, otherwise censoring at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

#Only when 20 events occurred according to Rivera inclusion criteria
if(sum(cens_pat1 == 0) + sum(cens_pat2 ==0) >= 20){

#evaluation for duration
Time_pat1 <- ifelse(Time_pat1 < duration, Time_pat1, duration)
Time_pat2 <- ifelse(Time_pat2 < duration, Time_pat2, duration)

#data for Cox model
data_Cox <- data.frame(time = c(Time_pat1, Time_pat2), 
                       cens = c(cens_pat1, cens_pat2), tx )  

#causing program to stop when something goes wrong
#causing program to stop when something wrong is happening
if(min(data_Cox$time) < 0){
  print("time below 0")
  Problem
  return()
}

#Cox model
a <- coxph(Surv(data_Cox$time, 1-data_Cox$cens) ~ tx)

#Storing results
results <- rbind(results, c(HbA1c_effect, a$coefficients, a$var))

}
}

#We use pearson here as prediction is important. 
#Correlation. We use Pearson here as prediction is important. 
#weighted for 1/var
names(results) <- c("surrogate", "target", "target_var")

boot.func <- function(dat, indices) {
data1=dat[indices,]

res <- weightedCorr(
data1$surrogate,
data1$target,
method = "Pearson",
weights = 1/data1$target_var,
ML = FALSE,
fast = TRUE
)
}

res.boot <- boot(results, boot.func, R=10000)  

#Storing into overall-results for duration
Overall_results <- rbind(Overall_results, 
c(duration, median(res.boot$t), quantile(res.boot$t, 0.025),
  quantile(res.boot$t, 0.975)))

}

#storing into data for the iterations
names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)
return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))
}


#Lower bound and upper bound here taken as mean as it is over simulations
R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  #R is 2nd element and then 4 elements further in a
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  #R lower bound is 3rd element and then 4 elements further in a
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  #R upper bound 4th element and then 4 elements further in a
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

write.csv(total_eval, "basecase1000_20events.csv")

```

Figure
```{r}

total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R mean"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R_agg$x

total_eval2$Group[11:20]<- "R LB"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R_LB_agg$x

total_eval2$Group[21:30]<- "R UB"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- R_UB_agg$x

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Basecase 20 events.jpeg")


```

#Relative risk survival 

In this simulation no censoring is taking place. As such, the relative risk can be computed as percentage death under active/percentage death under control. Only the point estimate is needed. 

```{r , include=FALSE}
set.seed(100)

#Rivera paper 
mean_HbA1c_effect <- -0.43
SD_HbA1c_effect <- 0.17
n_studies <- 19
#number per arm -> we assume equal studies in sample size
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000
#to have HR 0.8 as a mid point
beta <- 1.18

#dataset in which the results will be stored per duration
sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

a <- 
  foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot")) %dorng% {

    
iteration = 1    
#empty matrix in which the iterations results will be stored
Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
#evaluation from 1 to 10 year

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)

for (duration in 1:10){
#empty dataset to store results in for the 10 durations
results <- data.frame(matrix(ncol = 3, nrow = 0))

#creating trials
for (trial in 1: n_studies){

#HbA1c effect from normal distribution
HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)

#Mapping from HbA1c to underlying ln HR 
ln_HR <- HbA1c_effect*beta
#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)

#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]

#From percentage to time:
#Row to be used for percentages
elt_Clarke1 <- trunc(pat1/dist_Clarke)+1

#linear interpolation to obtain time point
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> percentage under control can be computed given HR
#that control percentage can be searched for (minus for ln HR to get to control)
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
#element that pat2_1 is reached
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
#computation time by interpolation
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]

#if Time_pat < duration then death, otherwise censoring at duration
#here we cause thus that time points equal to 1000 are censored at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

#Relative risk
RR <- (1- mean(cens_pat2))/(1- mean(cens_pat1))
log_RR <- log(RR)

#variance RR

a <- log_RR

IE <-  sum(1-cens_pat2)
IN <- sum(cens_pat2)
CE <-  sum(1-cens_pat1)
CN <-  sum(cens_pat1)
  
var_log_RR <- IN/(IE*(IE+IN))+ CN/(CE*(CE+CN))

#storage of results
results <- rbind(results, c(HbA1c_effect, a, var_log_RR))
}


results <- results[which(rowSums(is.na(results)) == 0),]
#Correlation. We use Pearson here as prediction is important. 
#weighted for 1/var
names(results) <- c("surrogate", "target", "target_var")


boot.func <- function(dat, indices) {
data1=dat[indices,]

res <- weightedCorr(
data1$surrogate,
data1$target,
method = "Pearson",
weights = 1/data1$target_var,
ML = FALSE,
fast = TRUE
)
}

res.boot <- boot(results, boot.func, R=10000)  

#Storing into overall-results for duration
Overall_results <- rbind(Overall_results, 
c(duration, median(res.boot$t), quantile(res.boot$t, 0.025),
  quantile(res.boot$t, 0.975)))

}

#Storing into data for the iterations
names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)

#returning duration, R, lower bound and upper bound
return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))

}

#a is created and is a list. 

R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  #2nd element is R, then every 4 times R is found back as list element in a
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
#aggregation over all iterations
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
#3rd element is R lower bound, then every 4 times R is found back as list element in a
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
#aggregation
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
#4th element is R upper bound, then every 4 times R is found back as list element in a
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
#aggregation over all iterations
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

write.csv(total_eval, "Relative_Risk.csv")

```


Plotting

```{r}

#Creating matrix in which results will be stored for plotting
total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

#R mean
total_eval2$Group[1:10]<- "R mean"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R_agg$x

#R lower bound
total_eval2$Group[11:20]<- "R LB"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R_LB_agg$x

#R upper bound
total_eval2$Group[21:30]<- "R UB"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- R_UB_agg$x

#plot
a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.43,0.73, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

#saving plot
ggsave("Relative Risk.jpeg")

```


#Risk difference

In this simulation no censoring is taking place. As such, the risk difference can be computed as percentage death under active/percentage death under control. Only the point estimate is needed. 

```{r , include=FALSE}
set.seed(100)

#Rivera paper 
mean_HbA1c_effect <- -0.43
SD_HbA1c_effect <- 0.17
n_studies <- 19
#number per arm -> we assume equal studies in sample size
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000
#to have HR 0.8 as a mid point
beta <- 1.18

#dataset in which the results will be stored per duration
sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

a <- 
  foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot")) %dorng% {
#empty matrix in which the iterations results will be stored
Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
#evaluation from 1 to 10 year

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)

for (duration in 1:10){
#empty dataset to store results in for the 10 durations
results <- data.frame(matrix(ncol = 3, nrow = 0))

#creating trials
for (trial in 1: n_studies){

#HbA1c effect from normal distribution
HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)

#Mapping from HbA1c to underlying ln HR 
ln_HR <- HbA1c_effect*beta
#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)

#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]

#From percentage to time:
#Row to be used for percentages
elt_Clarke1 <- trunc(pat1/dist_Clarke)+1

#linear interpolation to obtain time point
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> percentage under control can be computed given HR
#that control percentage can be searched for (minus for ln HR to get to control)
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
#element that pat2_1 is reached
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
#computation time by interpolation
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]

#if Time_pat < duration then death, otherwise censoring at duration
#here we cause thus that time points equal to 1000 are censored at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

#Risk difference
RD <- (1-mean(cens_pat2)) - (1- mean(cens_pat1))
a <- RD

EE <- sum(1-cens_pat2) 
EN <- sum(cens_pat2) 
CE <- sum(1-cens_pat1)
CN <- sum(cens_pat1)

var_RD <- EE*EN/(EE+EN)^3 +CE*CN/(CE+CN)^3

#storage of results
results <- rbind(results, c(HbA1c_effect, a, var_RD))
}

#Correlation. We use Pearson here as prediction is important. 
    #weighted for 1/var
    names(results) <- c("surrogate", "target", "target_var")
    
    boot.func <- function(dat, indices) {
      data1=dat[indices,]
      
      res <- weightedCorr(
        data1$surrogate,
        data1$target,
        method = "Pearson",
        weights = 1/data1$target_var,
        ML = FALSE,
        fast = TRUE
      )
    }
    
    res.boot <- boot(results, boot.func, R=10000)  
    
    #Storing into overall-results for duration
    Overall_results <- rbind(Overall_results, 
                             c(duration, median(res.boot$t),
                               quantile(res.boot$t, 0.025),
                               quantile(res.boot$t, 0.975)))
    
}

#Storing into data for the iterations
names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)

#returning duration, R, lower bound and upper bound
return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))

}

#a is created and is a list. 

R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  #2nd element is R, then every 4 times R is found back as list element in a
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
#aggregation over all iterations
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
#3rd element is R lower bound, then every 4 times R is found back as list element in a
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
#aggregation
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
#4th element is R upper bound, then every 4 times R is found back as list element in a
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
#aggregation over all iterations
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

write.csv(total_eval, "Risk Difference.csv")

```


Plotting

```{r}

#Creating matrix in which results will be stored for plotting
total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

#R mean
total_eval2$Group[1:10]<- "R mean"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R_agg$x

#R lower bound
total_eval2$Group[11:20]<- "R LB"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R_LB_agg$x

#R upper bound
total_eval2$Group[21:30]<- "R UB"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- R_UB_agg$x

#plot
a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.43,0.73, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

#saving plot
ggsave("Risk Difference.jpeg")

```


#Scenario Weibull
```{r , include=FALSE}
set.seed(100)

#Rivera paper 
mean_HbA1c_effect <- -0.43
SD_HbA1c_effect <- 0.17
n_studies <- 19
#number per arm -> we assume equal studies in sample size
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000
#to have HR 0.8 as a mid point
beta <- 1.18

#dataset in which the results will be stored per duration
sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

a <- 
  foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot", "flexsurv")) %dorng% {
#empty matrix in which the iterations results will be stored

Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
#evaluation from 1 to 10 year

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)

for (duration in 1:10){
#empty dataset to store results in for the 10 durations
results <- data.frame(matrix(ncol = 3, nrow = 0))

#creating trials
for (trial in 1: n_studies){

#HbA1c effect from normal distribution
HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)

#Mapping from HbA1c to underlying HR 
ln_HR <- HbA1c_effect*beta

#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]

#From percentage to time:
#Row to be used for percentages
elt_Clarke1 <- trunc(pat1/dist_Clarke)+1
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> percentage under control can be computed given HR
#that control percentage can be searched for (minus for ln HR to get to control)
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]

#if Time_pat < duration then death, otherwise censoring at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

Time_pat1 <- ifelse(Time_pat1 < duration, Time_pat1, duration)
Time_pat2 <- ifelse(Time_pat2 < duration, Time_pat2, duration)

data_Cox <- data.frame(time = c(Time_pat1, Time_pat2), 
                       cens = c(cens_pat1, cens_pat2), tx )  

#causing program to stop when something wrong is happening
if(min(data_Cox$time) < 0){
  print("time below 0")
  Problem
  return()
}

#Weibull distribution fitted
a <- flexsurvreg(Surv(data_Cox$time, 1-data_Cox$cens) ~ tx, 
                 dist = "weibull", inits = c(1,1,1))

cof_a <- a$coefficients[3]
var_a <- a$cov[3,3]
#adjusting for expected negative correlation 
results <- rbind(results, c(HbA1c_effect, -cof_a, var_a))
}

    #Correlation. We use Pearson here as prediction is important. 
    #weighted for 1/var
    names(results) <- c("surrogate", "target", "target_var")
    
    boot.func <- function(dat, indices) {
      data1=dat[indices,]
      
      res <- weightedCorr(
        data1$surrogate,
        data1$target,
        method = "Pearson",
        weights = 1/data1$target_var,
        ML = FALSE,
        fast = TRUE
      )
    }
    
    res.boot <- boot(results, boot.func, R=10000)  
    
    #Storing into overall-results for duration
    Overall_results <- rbind(Overall_results, 
                             c(duration, median(res.boot$t),
                               quantile(res.boot$t, 0.025),
                               quantile(res.boot$t, 0.975)))
    
}

#Storing into data for the iterations
names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)

return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))

}

R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

write.csv(total_eval, "basecase1000_Weibull.csv")



```


Plotting

```{r}

total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R mean"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R_agg$x

total_eval2$Group[11:20]<- "R LB"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R_LB_agg$x

total_eval2$Group[21:30]<- "R UB"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- R_UB_agg$x

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.43,0.73, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Basecase2 Weibull.jpeg")

```

#Scenario lognormal
```{r , include=FALSE}
set.seed(100)

#Rivera paper 
mean_HbA1c_effect <- -0.43
SD_HbA1c_effect <- 0.17
n_studies <- 19
#number per arm -> we assume equal studies in sample size
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000
#to have HR 0.8 as a mid point
beta <- 1.18

#dataset in which the results will be stored per duration
sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )


n_iterations <- 100
a <- 
  foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot", "flexsurv")) %dorng% {
#empty matrix in which the iterations results will be stored

Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
#evaluation from 1 to 10 year

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)

for (duration in 1:10){
#empty dataset to store results in for the 10 durations
results <- data.frame(matrix(ncol = 3, nrow = 0))

#creating trials
for (trial in 1: n_studies){

#HbA1c effect from normal distribution
HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)

#Mapping from HbA1c to underlying HR 
ln_HR <- HbA1c_effect*beta

#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]

#From percentage to time:
#Row to be used for percentages
elt_Clarke1 <- trunc(pat1/dist_Clarke)+1
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> percentage under control can be computed given HR
#that control percentage can be searched for (minus for ln HR to get to control)
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]

#if Time_pat < duration then death, otherwise censoring at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

Time_pat1 <- ifelse(Time_pat1 < duration, Time_pat1, duration)
Time_pat2 <- ifelse(Time_pat2 < duration, Time_pat2, duration)

data_Cox <- data.frame(time = c(Time_pat1, Time_pat2), 
                       cens = c(cens_pat1, cens_pat2), tx )  

#causing program to stop when something wrong is happening
if(min(data_Cox$time) < 0){
  print("time below 0")
  Problem
  return()
}
#lognormal
a <- flexsurvreg(Surv(data_Cox$time, 1-data_Cox$cens) ~ tx, dist = "lnorm", inits = c(1,1,1))

cof_a <- a$coefficients[3]
var_a <- a$cov[3,3]

results <- rbind(results, c(HbA1c_effect, -cof_a, var_a))
}


    #Correlation. We use Pearson here as prediction is important. 
    #weighted for 1/var
    names(results) <- c("surrogate", "target", "target_var")
    
    boot.func <- function(dat, indices) {
      data1=dat[indices,]
      
      res <- weightedCorr(
        data1$surrogate,
        data1$target,
        method = "Pearson",
        weights = 1/data1$target_var,
        ML = FALSE,
        fast = TRUE
      )
    }
    
    res.boot <- boot(results, boot.func, R=10000)  
    
    #Storing into overall-results for duration
    Overall_results <- rbind(Overall_results, 
                             c(duration, median(res.boot$t),
                               quantile(res.boot$t, 0.025),
                               quantile(res.boot$t, 0.975)))
    
}

#Storing into data for the iterations
names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)

return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))

}

R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

write.csv(total_eval, "basecase1000_lnorm.csv")


```


Plotting

```{r}

total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R mean"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R_agg$x

total_eval2$Group[11:20]<- "R LB"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R_LB_agg$x

total_eval2$Group[21:30]<- "R UB"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- R_UB_agg$x

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.43,0.73, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Basecase2 lognormal.jpeg")

```

#Loglogistic
```{r , include=FALSE}
set.seed(100)

#Rivera paper 
mean_HbA1c_effect <- -0.43
SD_HbA1c_effect <- 0.17
n_studies <- 19
#number per arm -> we assume equal studies in sample size
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 100
#to have HR 0.8 as a mid point
beta <- 1.18

#dataset in which the results will be stored per duration
sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

a <- 
  foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot", "flexsurv")) %dorng% {
#empty matrix in which the iterations results will be stored
Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)

#evaluation from 1 to 10 year
for (duration in 1:10){
#empty dataset to store results in for the 10 durations
results <- data.frame(matrix(ncol = 3, nrow = 0))

#creating trials
for (trial in 1: n_studies){

#HbA1c effect from normal distribution
HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)

#Mapping from HbA1c to underlying HR 
ln_HR <- HbA1c_effect*beta

#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]

#From percentage to time:
#Row to be used for percentages
elt_Clarke1 <- trunc(pat1/dist_Clarke)+1
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> percentage under control can be computed given HR
#that control percentage can be searched for (minus for ln HR to get to control)
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]

#if Time_pat < duration then death, otherwise censoring at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

Time_pat1 <- ifelse(Time_pat1 < duration, Time_pat1, duration)
Time_pat2 <- ifelse(Time_pat2 < duration, Time_pat2, duration)

data_Cox <- data.frame(time = c(Time_pat1, Time_pat2), 
                       cens = c(cens_pat1, cens_pat2), tx )  

#causing program to stop when something wrong is happening
if(min(data_Cox$time) < 0){
  print("time below 0")
  Problem
  return()
}

#loglogistic
a <- flexsurvreg(Surv(data_Cox$time, 1-data_Cox$cens) ~ tx, dist = "llogis", inits=c(1,1,1))

cof_a <- a$coefficients[3]
var_a <- a$cov[3,3]

results <- rbind(results, c(HbA1c_effect, -cof_a, var_a))
}

    #Correlation. We use Pearson here as prediction is important. 
    #weighted for 1/var
    names(results) <- c("surrogate", "target", "target_var")
    
    boot.func <- function(dat, indices) {
      data1=dat[indices,]
      
      res <- weightedCorr(
        data1$surrogate,
        data1$target,
        method = "Pearson",
        weights = 1/data1$target_var,
        ML = FALSE,
        fast = TRUE
      )
    }
    
    res.boot <- boot(results, boot.func, R=10000)  
    
    #Storing into overall-results for duration
    Overall_results <- rbind(Overall_results, 
                             c(duration, median(res.boot$t),
                               quantile(res.boot$t, 0.025),
                               quantile(res.boot$t, 0.975)))
    
}

#Storing into data for the iterations
names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)

return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))

}

R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

write.csv(total_eval, "basecase1000_llogis.csv")

```


Plotting

```{r}

total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R mean"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R_agg$x

total_eval2$Group[11:20]<- "R LB"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R_LB_agg$x

total_eval2$Group[21:30]<- "R UB"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- R_UB_agg$x

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.43,0.73, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Basecase2 loglogistic.jpeg")

```



#Function for scenario analyses

```{r , include=FALSE}

call_surrogacy_Cox <- function(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke){

set.seed(100)

sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

a <- 
  foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot")) %dorng% {
Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)

for (duration in 1:10){

results <- data.frame(matrix(ncol = 3, nrow = 0))

for (trial in 1: n_studies){

HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)
ln_HR <- HbA1c_effect*beta

#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]

elt_Clarke1 <- trunc(pat1/dist_Clarke)+1
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> first % to control 
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]


#if Time_pat < duration then death, otherwise censoring at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

Time_pat1 <- ifelse(Time_pat1 < duration, Time_pat1, duration)
Time_pat2 <- ifelse(Time_pat2 < duration, Time_pat2, duration)

data_Cox <- data.frame(time = c(Time_pat1, Time_pat2), 
                       cens = c(cens_pat1, cens_pat2), tx )  


#causing program to stop when something wrong is happening
if(min(data_Cox$time) < 0){
  print("time below 0")
  Problem
  return()
}
a <- coxph(Surv(data_Cox$time, 1-data_Cox$cens) ~ tx)

results <- rbind(results, c(HbA1c_effect, a$coefficients, a$var))
}


    #Correlation. We use Pearson here as prediction is important. 
    #weighted for 1/var
    names(results) <- c("surrogate", "target", "target_var")
    
    boot.func <- function(dat, indices) {
      data1=dat[indices,]
      
      res <- weightedCorr(
        data1$surrogate,
        data1$target,
        method = "Pearson",
        weights = 1/data1$target_var,
        ML = FALSE,
        fast = TRUE
      )
    }
    
    res.boot <- boot(results, boot.func, R=10000)  
    
    #Storing into overall-results for duration
    Overall_results <- rbind(Overall_results, 
                             c(duration, median(res.boot$t),
                               quantile(res.boot$t, 0.025),
                               quantile(res.boot$t, 0.975)))
    
}

names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)

return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))

}

R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

return(list(total_eval))
}



```



#Variations SD

SD 0.1

```{r}
SD_HbA1c_effect <- 0.1
beta <- 1.18
n_studies <- 19
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000

list1 <- call_surrogacy_Cox(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke)

meanR <- list1[[1]]

write.csv(meanR, "SD01_mean.csv")

```

SD 0.5

```{r}
SD_HbA1c_effect <- 0.5
beta <- 1.18
n_studies <- 19
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000

list1 <- call_surrogacy_Cox(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke)

meanR <- list1[[1]]

write.csv(meanR, "SD05_mean.csv")

```


Result are now in 
SD05_mean.csv
SD01_mean.csv
basecase1000.csv

Interest may be in both the mean R as well as the lower bound of R

```{r}
SD05_total_eval <- read.csv("SD05_mean.csv")
SD01_total_eval <- read.csv("SD01_mean.csv")
SD_base <- read.csv("basecase1000.csv")


#plot for mean
total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R SD05"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- SD05_total_eval$R_mean

total_eval2$Group[11:20]<- "R SD01"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- SD01_total_eval$R_mean

total_eval2$Group[21:30]<- "R base"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- SD_base$R_mean

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Mean correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("SD mean.jpeg")


#plot for lower bound
total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R SD05"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- SD05_total_eval$R_LB

total_eval2$Group[11:20]<- "R SD01"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- SD01_total_eval$R_LB

total_eval2$Group[21:30]<- "R base"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- SD_base$R_LB

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Mean lower bound correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("SD lower bound.jpeg")


```


#Variations beta

beta is 1.18
```{r}
SD_HbA1c_effect <- 0.17
beta <- 1.18
n_studies <- 19
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000

list1 <- call_surrogacy_Cox(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke)

meanR <- list1[[1]]

write.csv(meanR, "beta118_mean.csv")


```

beta 0.24
```{r}
SD_HbA1c_effect <- 0.17
beta <- 0.24
n_studies <- 19
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000

list1 <- call_surrogacy_Cox(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke)

meanR <- list1[[1]]

write.csv(meanR, "beta24_mean.csv")


```

data is now in 

beta24_mean.csv
beta118_mean.csv
basecase1000.csv

Interest may be in both the mean R as well as the lower bound of R

```{r}
rm(SD05_total_eval) 
rm(SD01_total_eval)

beta24 <- read.csv("beta24_mean.csv")
beta118 <- read.csv("beta118_mean.csv")
SD_base <- read.csv("basecase1000.csv")

#plot for mean

total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "HR 0.90"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- beta24$R_mean

total_eval2$Group[11:20]<- "HR 0.60"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- beta118$R_mean

total_eval2$Group[21:30]<- "R base"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- SD_base$R_mean

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Mean correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())


ggsave("beta mean.jpeg")

#plot for lower bound
total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R HR0.90"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- beta24$R_LB

total_eval2$Group[11:20]<- "R HR0.6"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- beta118$R_LB

total_eval2$Group[21:30]<- "R base"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- SD_base$R_LB

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Mean lower bound correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("beta lower bound.jpeg")


```


#Variations number of studies

n studies 50
```{r}
SD_HbA1c_effect <- 0.17
beta <- 1.18
n_studies <- 50
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000

list1 <- call_surrogacy_Cox(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke)

meanR <- list1[[1]]

write.csv(meanR, "n_studies50_mean.csv")


```


n_studies 250
```{r}
SD_HbA1c_effect <- 0.17
beta <- 1.18
n_studies <- 250
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000

list1 <- call_surrogacy_Cox(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke)

meanR <- list1[[1]]

write.csv(meanR, "n_studies250_mean.csv")

```

n studies 10
```{r}
SD_HbA1c_effect <- 0.17
beta <- 1.18
n_studies <- 10
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000

list1 <- call_surrogacy_Cox(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke)

meanR <- list1[[1]]

write.csv(meanR, "n_studies10_mean.csv")


```


data are now in 

n_studies50_mean.csv
n_studies250_mean.csv
basecase1000.csv

Interest may be in both the mean R as well as the lower bound of R

```{r}
rm(beta24) 
rm(beta118)

nst10 <- read.csv("n_studies10_mean.csv")
nst50 <- read.csv("n_studies50_mean.csv")
nst250 <- read.csv("n_studies250_mean.csv")
SD_base <- read.csv("basecase1000.csv")

#plot for mean

total_eval2 <- data.frame(matrix(nrow = 40, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "n studies 50"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- nst50$R_mean

total_eval2$Group[11:20]<- "n studies 250"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- nst250$R_mean

total_eval2$Group[21:30]<- "R base"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- SD_base$R_mean

total_eval2$Group[31:40]<- "n studies 10"
total_eval2$Duration[31:40]<- seq(1,10)
total_eval2$Value[31:40]<- nst10$R_mean


a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red","purple"))+
    labs(title ="Mean correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("number studies mean with 10.jpeg")


#plot for lower bound
total_eval2 <- data.frame(matrix(nrow = 40, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "n studies 50"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- nst50$R_LB

total_eval2$Group[11:20]<- "n studies 250"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- nst250$R_LB

total_eval2$Group[21:30]<- "R base"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- SD_base$R_LB

total_eval2$Group[31:40]<- "n studies 10"
total_eval2$Duration[31:40]<- seq(1,10)
total_eval2$Value[31:40]<- nst10$R_LB

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red", "purple"))+
    labs(title ="Mean lower bound correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("number studies lower bound with 10.jpeg")

```


#Variations n_arm

#Function for scenario analyses where problems are with no events

```{r , include=FALSE}

call_surrogacy_Cox_small <- function(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke){

set.seed(100)

sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

a <- 
  foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot")) %dorng% {
Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)

for (duration in 1:10){

results <- data.frame(matrix(ncol = 3, nrow = 0))

for (trial in 1: n_studies){

HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)
ln_HR <- HbA1c_effect*beta

#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]

elt_Clarke1 <- trunc(pat1/dist_Clarke)+1
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> first % to control 
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]


#if Time_pat < duration then death, otherwise censoring at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

Time_pat1 <- ifelse(Time_pat1 < duration, Time_pat1, duration)
Time_pat2 <- ifelse(Time_pat2 < duration, Time_pat2, duration)

data_Cox <- data.frame(time = c(Time_pat1, Time_pat2), 
                       cens = c(cens_pat1, cens_pat2), tx )  


#causing program to stop when something wrong is happening
if(min(data_Cox$time) < 0){
  print("time below 0")
  Problem
  return()
}
a <- coxph(Surv(data_Cox$time, 1-data_Cox$cens) ~ tx)

results <- rbind(results, c(HbA1c_effect, a$coefficients, a$var))
}

    results <- na.omit(results)
    #Correlation. We use Pearson here as prediction is important. 
    #weighted for 1/var
    names(results) <- c("surrogate", "target", "target_var")
    
    boot.func <- function(dat, indices) {
      data1=dat[indices,]
      
      res <- weightedCorr(
        data1$surrogate,
        data1$target,
        method = "Pearson",
        weights = 1/data1$target_var,
        ML = FALSE,
        fast = TRUE
      )
    }
    
    res.boot <- boot(results, boot.func, R=10000)  
    
    #Storing into overall-results for duration
    Overall_results <- rbind(Overall_results, 
                             c(duration, median(res.boot$t),
                               quantile(res.boot$t, 0.025),
                               quantile(res.boot$t, 0.975)))
    
}

names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)

return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))

}

R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

return(list(total_eval))
}



```



1000 patients per trial
```{r}
SD_HbA1c_effect <- 0.17
beta <- 1.18
n_studies <- 19
n_arm <- 1000/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000

list1 <- call_surrogacy_Cox_small(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke)

meanR <- list1[[1]]

write.csv(meanR, "n_pat1000_mean.csv")

```
10000 patients per trial
```{r}
SD_HbA1c_effect <- 0.17
beta <- 1.18
n_studies <- 19
n_arm <- 10000/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000

list1 <- call_surrogacy_Cox(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke)

meanR <- list1[[1]]

write.csv(meanR, "n_pat10000_mean.csv")

```

data are now in 
n_pat10000_mean.csv
n_pat1000_mean.csv
basecase1000.csv

Interest may be in both the mean R as well as the lower bound of R

```{r}
rm(nst50) 
rm(nst250)

trial1000 <- read.csv("n_pat1000_mean.csv")
trial10000 <- read.csv("n_pat10000_mean.csv")
SD_base <- read.csv("basecase1000.csv")

#plot for mean

total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "n study size 1,000"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- trial1000$R_mean

total_eval2$Group[11:20]<- "n study size 10,000"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- trial10000$R_mean

total_eval2$Group[21:30]<- "R base"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- SD_base$R_mean

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Mean correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("number arm mean.jpeg")


#plot for lower bound
total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[11:20]<- "n study size 1,000"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- trial1000$R_LB

total_eval2$Group[1:10]<- "n study size 10,000"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- trial10000$R_LB

total_eval2$Group[21:30]<- "R base"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- SD_base$R_LB

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Mean lower bound correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("number arm lower bound.jpeg")

```

#Variations R squared

function

```{r , include=FALSE}

#evaluation from 1 to 10 years
call_surrogacy_Cox_varR <- function(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke, R_squared){

set.seed(100)

sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

a <- 
  foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot")) %dorng% {

Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)

for (duration in 1:10){

results <- data.frame(matrix(ncol = 3, nrow = 0))

for (trial in 1: n_studies){

HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)
var_epsilon <- beta^2*SD_HbA1c_effect^2*(1-R_squared)/R_squared
error <- rnorm(1,0, sqrt(var_epsilon))

ln_HR <- HbA1c_effect*beta +error
#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]

#model to come from percentage to time:
elt_Clarke1 <- trunc(pat1/dist_Clarke)+1
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> first % to control 
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]


#if Time_pat < duration then death, otherwise censoring at duration

cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

Time_pat1 <- ifelse(Time_pat1 < duration, Time_pat1, duration)
Time_pat2 <- ifelse(Time_pat2 < duration, Time_pat2, duration)

data_Cox <- data.frame(time = c(Time_pat1, Time_pat2), 
                       cens = c(cens_pat1, cens_pat2), tx )  

#causing program to stop when something goes wrong
if(min(data_Cox$time) < 0){
  print("time below 0")
  Problem
  return()
}

a <- coxph(Surv(data_Cox$time, 1-data_Cox$cens) ~ tx)

results <- rbind(results, c(HbA1c_effect, a$coefficients, a$var))
}

    #Correlation. We use Pearson here as prediction is important. 
    #weighted for 1/var
    names(results) <- c("surrogate", "target", "target_var")
    
    boot.func <- function(dat, indices) {
      data1=dat[indices,]
      
      res <- weightedCorr(
        data1$surrogate,
        data1$target,
        method = "Pearson",
        weights = 1/data1$target_var,
        ML = FALSE,
        fast = TRUE
      )
    }
    
    res.boot <- boot(results, boot.func, R=10000)  
    
    #Storing into overall-results for duration
    Overall_results <- rbind(Overall_results, 
                             c(duration, median(res.boot$t),
                               quantile(res.boot$t, 0.025),
                               quantile(res.boot$t, 0.975)))
    
}

names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)
return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))

}

R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)

#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

return(list(total_eval))
}


```


R squared 0.9
```{r}
SD_HbA1c_effect <- 0.17
beta <- 1.18
n_studies <- 19
n_arm <- 7662/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000
R_squared<- 0.90

list1 <- call_surrogacy_Cox_varR(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke, R_squared)

meanR <- list1[[1]]

write.csv(meanR, "Rsquared90_mean.csv")

```


R squared 0.8
```{r}
SD_HbA1c_effect <- 0.17
beta <- 1.18
n_studies <- 19
n_arm <- 7662/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000
R_squared<- 0.80

list1 <- call_surrogacy_Cox_varR(SD_HbA1c_effect, beta, 
n_studies, n_arm, tx, n_iterations, mean_HbA1c_effect, dist_Clarke, Clarke, R_squared)

meanR <- list1[[1]]

write.csv(meanR, "Rsquared80_mean.csv")

```

data are now in

Rsquared90_mean.csv
Rsquared80_mean.csv
basecase1000.csv

Interest may be in both the mean R as well as the lower bound of R

```{r}
rm(trial1000) 
rm(trial10000)

R2_90 <- read.csv("Rsquared90_mean.csv")
R2_80 <- read.csv("Rsquared80_mean.csv")
SD_base <- read.csv("basecase1000.csv")

#plot for mean

total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R squared 0.90"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R2_90$R_mean

total_eval2$Group[11:20]<- "R squared 0.80"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R2_80$R_mean

total_eval2$Group[21:30]<- "R base"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- SD_base$R_mean

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Mean correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("R squared mean.jpeg")


#plot for lower bound
total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R squared 0.90"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R2_90$R_LB

total_eval2$Group[11:20]<- "R squared 0.80"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R2_80$R_LB

total_eval2$Group[21:30]<- "R base"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- SD_base$R_LB

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Mean lower bound correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(round(min(total_eval2$Value),2), 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(min(total_eval2$Value), 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("R squared LB.jpeg")


```


#One year survival percentage 
10%
25%
50%
75%
90%

```{r}

#Percentage at 1 from Clarke to 10%
#Exact percentage at 1:
row_1 <- sum(Time<1)
perc_1 <- (1-Time[row_1])/(Time[row_1+1]-Time[row_1])*
(Cum_death[row_1+1]-Cum_death[row_1])+Cum_death[row_1]

#HR for 10%: 
HR10 <- log(.90)/log(1-perc_1)
1- (1-perc_1)^HR10
HR25 <- log(.75)/log(1-perc_1)
1- (1-perc_1)^HR25
HR50 <- log(.50)/log(1-perc_1)
1- (1-perc_1)^HR50
HR75 <- log(.25)/log(1-perc_1)
1- (1-perc_1)^HR75
HR90 <- log(.10)/log(1-perc_1)
1- (1-perc_1)^HR90

Cum_death10 <- 1-(1-Cum_death)^HR10
Cum_death25 <- 1-(1-Cum_death)^HR25
Cum_death50 <- 1-(1-Cum_death)^HR50
Cum_death75 <- 1-(1-Cum_death)^HR75
Cum_death90 <- 1-(1-Cum_death)^HR90

#Figure
plot_perc <- data.frame(matrix(nrow = 0, ncol = 3))
names(plot_perc) <- c("Time", "Death", "group")
Cum_death_group <- data.frame(matrix(nrow = length(Cum_death), ncol = 1))
names(Cum_death_group) <- "group"
Cum_death_group$group <- "Clarke"
Cum_death_group$group <- as.character(Cum_death_group$group)
plot_perc <- rbind(plot_perc, cbind(Time, Cum_death, Cum_death_group$group))
names(plot_perc)[3] <- "group"

mat10 <- data.frame(matrix(nrow = 36, ncol = 3))
names(mat10)<- names(plot_perc)
mat10[,1] <- Time
mat10[,2] <- Cum_death10
mat10[,3] <- "One year 10%"
plot_perc <- rbind(plot_perc, mat10)

mat25 <- mat10
mat25[,2] <- Cum_death25
mat25[,3] <- "One year 25%"
plot_perc <- rbind(plot_perc, mat25)

mat50 <- mat10
mat50[,2] <- Cum_death50
mat50[,3] <- "One year 50%"
plot_perc <- rbind(plot_perc, mat50)
  
mat75 <- mat10
mat75[,2] <- Cum_death75
mat75[,3] <- "One year 75%"
plot_perc <- rbind(plot_perc, mat75)

mat90 <- mat10
mat90[,2] <- Cum_death90
mat90[,3] <- "One year 90%"
plot_perc <- rbind(plot_perc, mat90)

cpb2 <- c("#000000", "#E69F00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

plot_perc$S <- 1 - as.numeric(plot_perc$Cum_death)
plot_perc$group <- as.character(plot_perc$group)
plot_perc$S <- as.numeric(plot_perc$S)
plot_perc$Time <- as.numeric(plot_perc$Time)

a <- ggplot(plot_perc
, aes(Time, S,colour=group, size = group, type = group)) + 
  geom_line(aes(linetype=group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=cpb2)+
    labs(title ="Survival percentages")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("twodash","solid","longdash","dotted","dotdash","dashed"))+
  labs(y="Survival percentage")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(0, 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Survival percentages.jpeg")

```


#For 10

```{r , include=FALSE}


Clarke <- data.frame(matrix(nrow = 10000, ncol = 2))
for(i in 1: 10000){

  start_d <- sum(Cum_death10 < i/10000)
  if (start_d>0){ 
  Clarke[i,1] <- i/10000
  Clarke[i,2] <- 
  (i/10000 - Cum_death10[start_d])/(Cum_death10[start_d+1]-Cum_death10[start_d])*
  (Time[start_d+1]-Time[start_d])+Time[start_d]
  }
  if (start_d == 0){
  Clarke[i,1] <- i/10000
  Clarke[i,2] <- 
  (i/10000)/(Cum_death10[1])*(Time[1])
  
  }
  
}
plot(Clarke[,1], Clarke[,2])

dist_Clarke <- Clarke[2,1] - Clarke[1,1]
Clarke[,2]<-ifelse(is.na(Clarke[,2]), 1000, Clarke[,2])
Clarke <- rbind(c(0,0), Clarke)
#For computational simplicity
Clarke <- rbind(Clarke, c(1.1,1000))

set.seed(100)

#Rivera paper 
mean_HbA1c_effect <- -0.43
SD_HbA1c_effect <- 0.17
n_studies <- 19
#number per arm -> we assume equal studies in sample size
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))
n_iterations <- 1000

#to have HR 0.8 as a mid point
beta <- 1.18

#dataset in which the results will be stored per duration
sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

a <- 
  foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot")) %dorng% {
#empty matrix in which the iterations results will be stored

Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)


#evaluation from 1 to 10 year
for (duration in 1:10){

#empty dataset to store results in for the 10 durations
results <- data.frame(matrix(ncol = 3, nrow = 0))

#creating trials
for (trial in 1: n_studies){

#HbA1c effect from normal distribution
HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)

#Mapping from HbA1c to underlying HR 
ln_HR <- HbA1c_effect*beta

#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]


#From percentage to time:
elt_Clarke1 <- trunc(pat1/dist_Clarke)+1
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> first % to control 
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1

Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]


#if Time_pat < duration then death, otherwise censoring at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

Time_pat1 <- ifelse(Time_pat1 < duration, Time_pat1, duration)
Time_pat2 <- ifelse(Time_pat2 < duration, Time_pat2, duration)

data_Cox <- data.frame(time = c(Time_pat1, Time_pat2), 
                       cens = c(cens_pat1, cens_pat2), tx )  

#causing program to stop when something wrong is happening
if(min(data_Cox$time) < 0){
  print("time below 0")
  Problem
  return()
}

#Cox model
a <- coxph(Surv(data_Cox$time, 1-data_Cox$cens) ~ tx)

results <- rbind(results, c(HbA1c_effect, a$coefficients, a$var))
}
    #Correlation. We use Pearson here as prediction is important. 
    #weighted for 1/var
    names(results) <- c("surrogate", "target", "target_var")
    
    boot.func <- function(dat, indices) {
      data1=dat[indices,]
      
      res <- weightedCorr(
        data1$surrogate,
        data1$target,
        method = "Pearson",
        weights = 1/data1$target_var,
        ML = FALSE,
        fast = TRUE
      )
    }
    
    res.boot <- boot(results, boot.func, R=10000)  
    
    #Storing into overall-results for duration
    Overall_results <- rbind(Overall_results, 
                             c(duration, median(res.boot$t),
                               quantile(res.boot$t, 0.025),
                               quantile(res.boot$t, 0.975)))
    
}

#storing into data for the iterations
names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)
return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))

}


R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

write.csv(total_eval, "One_year_10.csv")

```

```{r}

total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R mean"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R_agg$x

total_eval2$Group[11:20]<- "R LB"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R_LB_agg$x

total_eval2$Group[21:30]<- "R UB"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- R_UB_agg$x

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(0, 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Ten percent.jpeg")


```


#For 25

```{r , include=FALSE}

Clarke <- data.frame(matrix(nrow = 10000, ncol = 2))
for(i in 1: 10000){

  start_d <- sum(Cum_death25 < i/10000)
  if (start_d>0){ 
  Clarke[i,1] <- i/10000
  Clarke[i,2] <- 
  (i/10000 - Cum_death25[start_d])/(Cum_death25[start_d+1]-Cum_death25[start_d])*
  (Time[start_d+1]-Time[start_d])+Time[start_d]
  }
  if (start_d == 0){
  Clarke[i,1] <- i/10000
  Clarke[i,2] <- 
  (i/10000)/(Cum_death25[1])*(Time[1])
  
  }
  
}
plot(Clarke[,2], 1-Clarke[,1])

dist_Clarke <- Clarke[2,1] - Clarke[1,1]

Clarke[,2]<-ifelse(is.na(Clarke[,2]), 1000, Clarke[,2])
Clarke <- rbind(c(0,0), Clarke)
#For computational simplicity
Clarke <- rbind(Clarke, c(1.1,1000))
set.seed(100)

#Rivera paper 
mean_HbA1c_effect <- -0.43
SD_HbA1c_effect <- 0.17
n_studies <- 19
#number per arm -> we assume equal studies in sample size
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))

#to have HR 0.8 as a mid point
beta <- 1.18

#evaluation from 1 to 10 years

#dataset in which the results will be stored per duration
sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

a <- 
  foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot")) %dorng% {

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)
  
  
#empty matrix in which the iterations results will be stored
Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))

#evaluation from 1 to 10 year
for (duration in 1:10){

#empty dataset to store results in for the 10 durations
results <- data.frame(matrix(ncol = 3, nrow = 0))

#creating trials
for (trial in 1: n_studies){

#HbA1c effect from normal distribution
HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)

#Mapping from HbA1c to underlying HR 
ln_HR <- HbA1c_effect*beta

#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]


#From percentage to time:
elt_Clarke1 <- trunc(pat1/dist_Clarke)+1
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> first % to control 
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]

#if Time_pat < duration then death, otherwise censoring at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

Time_pat1 <- ifelse(Time_pat1 < duration, Time_pat1, duration)
Time_pat2 <- ifelse(Time_pat2 < duration, Time_pat2, duration)

data_Cox <- data.frame(time = c(Time_pat1, Time_pat2), 
                       cens = c(cens_pat1, cens_pat2), tx )  


#causing program to stop when something wrong is happening
if(min(data_Cox$time) < 0){
  print("time below 0")
  Problem
  return()
}

a <- coxph(Surv(data_Cox$time, 1-data_Cox$cens) ~ tx)

results <- rbind(results, c(HbA1c_effect, a$coefficients, a$var))
}

    #Correlation. We use Pearson here as prediction is important. 
    #weighted for 1/var
    names(results) <- c("surrogate", "target", "target_var")
    
    boot.func <- function(dat, indices) {
      data1=dat[indices,]
      
      res <- weightedCorr(
        data1$surrogate,
        data1$target,
        method = "Pearson",
        weights = 1/data1$target_var,
        ML = FALSE,
        fast = TRUE
      )
    }
    
    res.boot <- boot(results, boot.func, R=10000)  
    
    #Storing into overall-results for duration
    Overall_results <- rbind(Overall_results, 
                             c(duration, median(res.boot$t),
                               quantile(res.boot$t, 0.025),
                               quantile(res.boot$t, 0.975)))
    
}

#storing into data for the terations
names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)
return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))

}


R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

write.csv(total_eval, "One_year25.csv")

```

```{r}

total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R mean"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R_agg$x

total_eval2$Group[11:20]<- "R LB"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R_LB_agg$x

total_eval2$Group[21:30]<- "R UB"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- R_UB_agg$x

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(0, 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Twentyfive percent.jpeg")


```



#For 50



```{r , include=FALSE}

Clarke <- data.frame(matrix(nrow = 10000, ncol = 2))
for(i in 1: 10000){

  start_d <- sum(Cum_death50 < i/10000)
  if (start_d>0){ 
  Clarke[i,1] <- i/10000
  Clarke[i,2] <- 
  (i/10000 - Cum_death50[start_d])/(Cum_death50[start_d+1]-Cum_death50[start_d])*
  (Time[start_d+1]-Time[start_d])+Time[start_d]
  }
  if (start_d == 0){
  Clarke[i,1] <- i/10000
  Clarke[i,2] <- 
  (i/10000)/(Cum_death50[1])*(Time[1])
  
  }
  
}
plot(Clarke[,2], 1-Clarke[,1])

dist_Clarke <- Clarke[2,1] - Clarke[1,1]
Clarke[,2]<-ifelse(is.na(Clarke[,2]), 1000, Clarke[,2])


Clarke <- rbind(c(0,0), Clarke)
#For computational simplicity
Clarke <- rbind(Clarke, c(1.1,1000))
set.seed(100)

#Rivera paper 
mean_HbA1c_effect <- -0.43
SD_HbA1c_effect <- 0.17
n_studies <- 19
#number per arm -> we assume equal studies in sample size
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))

#to have HR 0.8 as a mid point
beta <- 1.18

#evaluation from 1 to 10 years

#dataset in which the results will be stored per duration
sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

a <- 
  foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot")) %dorng% {
#empty matrix in which the iterations results will be stored
Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)


#evaluation from 1 to 10 year
for (duration in 1:10){

#empty dataset to store results in for the 10 durations
results <- data.frame(matrix(ncol = 3, nrow = 0))

#creating trials
for (trial in 1: n_studies){

#HbA1c effect from normal distribution
HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)

#Mapping from HbA1c to underlying HR 
ln_HR <- HbA1c_effect*beta

#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]


#From percentage to time:
elt_Clarke1 <- trunc(pat1/dist_Clarke)+1
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> first % to control 
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]

#if Time_pat < duration then death, otherwise censoring at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

Time_pat1 <- ifelse(Time_pat1 < duration, Time_pat1, duration)
Time_pat2 <- ifelse(Time_pat2 < duration, Time_pat2, duration)

data_Cox <- data.frame(time = c(Time_pat1, Time_pat2), 
                       cens = c(cens_pat1, cens_pat2), tx )  

#causing program to stop when something wrong is happening
if(min(data_Cox$time) < 0){
  print("time below 0")
  Problem
  return()
}

a <- coxph(Surv(data_Cox$time, 1-data_Cox$cens) ~ tx)

results <- rbind(results, c(HbA1c_effect, a$coefficients, a$var))
}

  
    #Correlation. We use Pearson here as prediction is important. 
    #weighted for 1/var
    names(results) <- c("surrogate", "target", "target_var")
    
    boot.func <- function(dat, indices) {
      data1=dat[indices,]
      
      res <- weightedCorr(
        data1$surrogate,
        data1$target,
        method = "Pearson",
        weights = 1/data1$target_var,
        ML = FALSE,
        fast = TRUE
      )
    }
    
    res.boot <- boot(results, boot.func, R=10000)  
    
    #Storing into overall-results for duration
    Overall_results <- rbind(Overall_results, 
                             c(duration, median(res.boot$t),
                               quantile(res.boot$t, 0.025),
                               quantile(res.boot$t, 0.975)))
    
}

#storing into data for the iterations
names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)
return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))

}


R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

write.csv(total_eval, "One_year_50.csv")

```

```{r}

total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R mean"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R_agg$x

total_eval2$Group[11:20]<- "R LB"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R_LB_agg$x

total_eval2$Group[21:30]<- "R UB"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- R_UB_agg$x

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(0, 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Fifty percent.jpeg")

```



#For 75

```{r , include=FALSE}
Clarke <- data.frame(matrix(nrow = 10000, ncol = 2))
for(i in 1: 10000){

  start_d <- sum(Cum_death75 < i/10000)
  if (start_d>0){ 
  Clarke[i,1] <- i/10000
  Clarke[i,2] <- 
  (i/10000 - Cum_death75[start_d])/(Cum_death75[start_d+1]-Cum_death75[start_d])*
  (Time[start_d+1]-Time[start_d])+Time[start_d]
  }
  if (start_d == 0){
  Clarke[i,1] <- i/10000
  Clarke[i,2] <- 
  (i/10000)/(Cum_death75[1])*(Time[1])
  
  }
  
}
plot(Clarke[,2], 1-Clarke[,1])

dist_Clarke <- Clarke[2,1] - Clarke[1,1]

Clarke[,2]<-ifelse(is.na(Clarke[,2]), 1000, Clarke[,2])

set.seed(100)
Clarke <- rbind(c(0,0), Clarke)
#For computational simplicity
Clarke <- rbind(Clarke, c(1.1,1000))

#Rivera paper 
mean_HbA1c_effect <- -0.43
SD_HbA1c_effect <- 0.17
n_studies <- 19
#number per arm -> we assume equal studies in sample size
n_arm <- 7226/2
tx <- c(rep(0, n_arm), rep(1, n_arm))

#to have HR 0.8 as a mid point
beta <- 1.18

#evaluation from 1 to 10 years

#dataset in which the results will be stored per duration
sim_Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))
names(sim_Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )

a <- 
  foreach(iteration = 1: n_iterations, .combine = 'c', .options.RNG=123, .packages= c("survival", "wCorr", "metafor", "boot")) %dorng% {
#empty matrix in which the iterations results will be stored
Overall_results <- data.frame(matrix(ncol = 4, nrow = 0))

#creation of the survival percentages for the patients in the trials
pat1_iteration <- runif(n_arm*n_studies)
pat2_iteration <- runif(n_arm*n_studies)


#evaluation from 1 to 10 year
for (duration in 1:10){

#empty dataset to store results in for the 10 durations
results <- data.frame(matrix(ncol = 3, nrow = 0))

#creating trials
for (trial in 1: n_studies){

#HbA1c effect from normal distribution
HbA1c_effect <- rnorm(1, mean_HbA1c_effect, SD_HbA1c_effect)

#Mapping from HbA1c to underlying HR 
ln_HR <- HbA1c_effect*beta

#creation of the survival percentages for the patients in the trial
#for all durations we use the same patients set up, so that fluctuations
#are solely due to duration and not due to sampling new patients
pat1 <- pat1_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]
pat2 <- pat2_iteration[c((1+(trial-1)*n_arm):(trial*n_arm))]

#From percentage to time:
elt_Clarke1 <- trunc(pat1/dist_Clarke)+1
Time_pat1 <- (pat1-Clarke[elt_Clarke1,1])/dist_Clarke*
  (Clarke[elt_Clarke1+1,2]-Clarke[elt_Clarke1,2])+Clarke[elt_Clarke1,2]

#Active arm -> first % to control 
pat2_1 <- 1- (1-pat2)^(exp(-ln_HR))
elt_Clarke2 <- trunc(pat2_1/dist_Clarke)+1
Time_pat2 <- (pat2_1-Clarke[elt_Clarke2,1])/dist_Clarke*
  (Clarke[elt_Clarke2+1,2]-Clarke[elt_Clarke2,2])+Clarke[elt_Clarke2,2]

#if Time_pat < duration then death, otherwise censoring at duration
cens_pat1 <- ifelse(Time_pat1 < duration, 0, 1)
cens_pat2 <- ifelse(Time_pat2 < duration, 0, 1)

Time_pat1 <- ifelse(Time_pat1 < duration, Time_pat1, duration)
Time_pat2 <- ifelse(Time_pat2 < duration, Time_pat2, duration)

data_Cox <- data.frame(time = c(Time_pat1, Time_pat2), 
                       cens = c(cens_pat1, cens_pat2), tx )  

#causing program to stop when something wrong is happening
if(min(data_Cox$time) < 0){
  print("time below 0")
  Problem
  return()
}

a <- coxph(Surv(data_Cox$time, 1-data_Cox$cens) ~ tx)

results <- rbind(results, c(HbA1c_effect, a$coefficients, a$var))
}

    #Correlation. We use Pearson here as prediction is important. 
    #weighted for 1/var
    names(results) <- c("surrogate", "target", "target_var")
    
    boot.func <- function(dat, indices) {
      data1=dat[indices,]
      
      res <- weightedCorr(
        data1$surrogate,
        data1$target,
        method = "Pearson",
        weights = 1/data1$target_var,
        ML = FALSE,
        fast = TRUE
      )
    }
    
    res.boot <- boot(results, boot.func, R=10000)  
    
    #Storing into overall-results for duration
    Overall_results <- rbind(Overall_results, 
                             c(duration, median(res.boot$t),
                               quantile(res.boot$t, 0.025),
                               quantile(res.boot$t, 0.975)))
    
}

#storing into data for the iterations
names(Overall_results) <- c("Duration","R", "Lower bound", "Upper bound" )
sim_Overall_results <- rbind(sim_Overall_results, Overall_results)

return(list(Overall_results$Duration, Overall_results$R, Overall_results[,3], Overall_results[,4]))
}

R <- data.frame(matrix(nrow = 0, ncol = 2))
names(R) <- c("Duration", "R")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R <- a[[2+4*(i-1)]]
  R <- rbind(R, temp1)  
}
R_agg <-aggregate(R$R, list(R$Duration), mean)

#Lower bound and upper bound here taken as mean as it is over simulations

R_LB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_LB) <- c("Duration", "R_LB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_LB <- a[[3+4*(i-1)]]
  R_LB <- rbind(R_LB, temp1)  
}
R_LB_agg <- aggregate(R_LB$R_LB, list(R_LB$Duration), mean)

R_UB <- data.frame(matrix(nrow = 0, ncol = 2))
names(R_UB) <- c("Duration", "R_UB")
for (i in 1: n_iterations){
  temp1 <- data.frame(matrix(nrow = 10, ncol = 0))
  temp1$Duration <- seq(1:10)
  temp1$R_UB <- a[[4+4*(i-1)]]
  R_UB <- rbind(R_UB, temp1)  
}
R_UB_agg <-aggregate(R_UB$R_UB, list(R_UB$Duration), mean)


#Putting the numbers in one matrix
total_eval <- data.frame(matrix(nrow = 10, ncol = 4))
total_eval$X1 <- as.numeric(seq(1,10))
total_eval$X2 <- as.numeric(R_agg$x)
total_eval$X3 <- as.numeric(R_LB_agg$x)
total_eval$X4 <- as.numeric(R_UB_agg$x)
names(total_eval) <- c("Years", "R_mean", "R_LB", "R_UB")

write.csv(total_eval, "One_year_75.csv")

```

```{r}

total_eval2 <- data.frame(matrix(nrow = 30, ncol = 3))
names(total_eval2) <- c("Group", "Duration", "Value")

total_eval2$Group[1:10]<- "R mean"
total_eval2$Duration[1:10]<- seq(1,10)
total_eval2$Value[1:10]<- R_agg$x

total_eval2$Group[11:20]<- "R LB"
total_eval2$Duration[11:20]<- seq(1,10)
total_eval2$Value[11:20]<- R_LB_agg$x

total_eval2$Group[21:30]<- "R UB"
total_eval2$Duration[21:30]<- seq(1,10)
total_eval2$Value[21:30]<- R_UB_agg$x

a <- ggplot(total_eval2
, aes(Duration, Value,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,2,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red"))+
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(0, 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Seventyfive percent.jpeg")

```




```{r}
seventyfive <- read.csv( "One_year_75.csv")
seventyfive$group <- "75%"

fifty <- read.csv( "One_year_50.csv")
fifty$group <- "50%"

Twentyfive <- read.csv( "One_year25.csv")
Twentyfive$group <- "25%"

Ten <- read.csv( "One_year_10.csv")
Ten$group <- "10%"

basecase <- read.csv( "basecase1000.csv")
basecase$group <- "basecase"

plot_all <- rbind(
   seventyfive, fifty, Twentyfive, Ten,basecase)

plot_all$Group <- plot_all$group

library(ggsci)

a <- ggplot(plot_all
, aes(Years, R_LB,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,.8,.8,.8,.8,.8,.8,.8,1,1,1))+
#  scale_color_manual(values=scale_fill_lancet())+
  scale_color_lancet() +
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("solid", "dashed", "dotted", "dotdash", "longdash", "twodash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c( 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(0, 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Baseperc LB.jpeg")



a <- ggplot(plot_all
, aes(Years, R_mean,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,.8,.8,.8,.8,.8,.8,.8,1,1,1))+
#  scale_color_manual(values=scale_fill_lancet())+
  scale_color_lancet() +
    labs(title ="Correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("solid", "dashed", "dotted", "dotdash", "longdash", "twodash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c( 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(0, 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Baseperc mean.jpeg")


```



```{r}
Weibull <- read.csv( "basecase1000_Weibull.csv")
Weibull$group <- "Weibull"

lognormal <- read.csv( "basecase1000_lnorm.csv")
lognormal$group <- "log normal"

llogis <- read.csv( "basecase1000_llogis.csv")
llogis$group <- "Loglogistic"

basecase <- read.csv( "basecase1000.csv")
basecase$group <- "basecase"

plot_all <- rbind(
  Weibull, lognormal, llogis, basecase)

plot_all$Group <- plot_all$group

library(ggsci)


a <- ggplot(plot_all
, aes(Years, R_LB,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,.8,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red", "blue"))+
    labs(title ="Mean lower bound correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(0, 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(-.2, 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Base_dist LB.jpeg")

a <-ggplot(plot_all
, aes(Years, R_mean,colour=Group, size = Group, type = Group)) + 
  geom_line(aes(linetype=Group)) + 
  scale_size_manual(values=c(.8, .8,.8,.8,.8,.8,.8,.8,.8,.8,1,1,1))+
  scale_color_manual(values=c("darkgreen", "black", "red", "blue"))+
    labs(title ="Mean correlation as function of trial duration")+
  labs(x  = "Time (years)" ) +
  scale_linetype_manual(values=c("dashed", "dotted", "twodash", "longdash", "solid", "longdash", "dashed", "solid", "solid", "solid", "dashed", "longdash", "longdash"))+
  labs(y="Correlation")+
  scale_x_continuous(breaks=c(0, 1,2,2.6,4,5,6,7,8,9,10))+
  scale_y_continuous(breaks=c(0, 0, 0.25,0.45,0.75, 0.85, 1))+
  coord_cartesian(expand = FALSE,ylim = c(0, 1), xlim = c(0, 10)) +
  theme_bw()
a+ theme(panel.grid.minor = element_blank())

ggsave("Base_dist mean.jpeg")

```



